Search-Based Test Data Generation for JavaScript Functions that Interact with the DOM

### 2018-01-29 doc/icse2018/icse2018.tex
Working on Related work section

\usepackage{tablefootnote}
\usepackage{syntax}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{booktabs} % For formal tables
\usepackage{tikz}
\usetikzlibrary{arrows,shadows,positioning,decorations.pathmorphing}
\usepackage{pgf-umlsd}
\usepackage{tikz-uml}
\usepackage{hyperref}
\usepackage{upquote}
\usepackage{listings}
\usepackage{lsthaskell}
\usepackage{xspace}
\usepackage{mdframed}
\usepackage{algorithmic}
\usepackage{longtable}
\usepackage{subcaption}
\usepackage{pgfplots}
\pgfplotsset{compat=newest}
\usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = red, %Colour of internal links
  citecolor    = green %Colour of citations
}

@@

\begin{document}
\title{Search-Based Test Data Generation for JavaScript Functions with DOM}

@@

\begin{abstract}
As of 2017 JavaScript and Node.js continue to stay the most prevalent technologies according to the Stack Overflow developers survey. Nevertheless, existing JS testing frameworks are still lacking any support for such a vital step in test automation as the generation of input data. To address this problem, we present a novel \textbf{J}avascript \textbf{E}volutionary-based testing framework with \textbf{D}OM as an \textbf{I}input, called \textbf{JEDI}. In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function including global DOM state. The \emph{genetic with restart} algorithm, proposed in this paper, was able to achieve complete branch coverage in our empirical evaluation with the average execution time 7.7 sec. per branch 
\end{abstract}

@@

Over the past two decades search-based test data generation has proven to be one of the most effective solutions for a wide range of technologies including object-oriented~\cite{paper}, web~\cite{paper} and mobile~\cite{paper}. In recent years, some effort was made to apply search-based testing to dynamic languages such as Python~\cite{paper}, Ruby~\cite{paper} (maybe mention Go and Lua), but to the best of our knowledge search-based testing approach has never been applied to JavaScript. Our work makes the following contributions:
\begin{enumerate}
\item The \emph{JEDI} framework is a novel JS unit testing tool using search-based techniques for generating test data. Notably, our testing framework is able to generate an arbitrary DOM input, which is syntactically valid and compliant with the recent HTML5 specification.   
\item We propose a novel test generation algorithm, called ``genetic with restart'', combining the benefits of systematic fitness improvement with the genetic search and the ability of escaping plateau by restarting search with a new target.
\item Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conduced an empirical validation of our framework and performed a significance study of the results. The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency...  
\end{enumerate}

@@

\begin{figure}[t]
\setlength{\grammarparsep}{3pt}
\small
\begin{grammar}

@@

<Array Type> ::= [ <Primitive Type> ] | [ <Array Type> ]
\end{grammar}
\caption{Grammar of supported JS type annotations}
\label{fig.js.type.annot}
\end{figure}

@@

In order to evaluate the feasibility of our test framework adoption in practice, we conducted an empirical evaluation on a set of case-studies described in Section~\ref{sub.sec.case.studies}. All experiments were submitted as a batch mode job on a cluster machine with 32 HT Cores and 256 GB RAM running under Scientific Linux 7.3. We have created three different instances of the JS testing framework --- each is based on a slight variation of the underlying genetic search algorithm. The first version, which play the role of our baseline, is \emph{Random} ($\Random$). Instead of applying crossover and mutation to evolve the population, this algorithm regenerates the new population randomly from scratch. It is worth to notice, that the random version also benefits from both preliminary static analysis phase and dynamic constant propagation as part of the fitness evaluation. The second version is \emph{Genetic}~($\Genetic$) --- it literally follows all of the steps prescribed by the genetic framework in Figure~\ref{fig.framework.architect}. The last version is the \emph{Genetic with Restart} ($\RGenetic$). It is based on the genetic algorithm~\ref{alg.gen} where the search is restarted after the archives are converged within a certain history window. On one hand, the smaller window size forces the GA to converge faster and early discovers the stagnation on a flat space. On the other hand, the small window can lead to a premature archive convergence, which prevents the right genetic combination from been triggered. We have experimented with two different windows of size 5 and 10. But since the latter one ($\RGenetic$) showed the best performance over all, we chose it to report in the paper. Table~\ref{tbl.gen.config} summarizes the configuration parameters for all three versions of the testing framework. The initial setup for genetic algorithm is similar to other frameworks, e.g. \emph{EvoSuite}~\cite{evosuite}.

@@

By carrying the evaluation, we would like to address the following research questions:
\begin{description}
\item[\textbf{RQ1 (effectiveness):}] What is the value of branch coverage achieved by our testing framework? Which testing algorithm is the most effective?
\item[\textbf{RQ2 (efficiency):}] How efficient our testing framework? And which algorithm is the most efficient?
\item[\textbf{RQ3 (significance):}] What is statistical significance and effect size of our experimental results? 
\end{description}

@@

\begin{table}[!t]
  \caption{Result Summary (L - large, M - medium, S - small)}
  \label{tbl.stats.sum}
    \footnotesize
    \begin{tabular}{l|ccc|ccc|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}}
      \toprule
      \multirow{3}{*}{\textbf{TYPE}} &  \multicolumn{3}{c|}{\textbf{coverage (\%)}} & \multicolumn{3}{c|}{\textbf{time (sec.)}} & \multicolumn{9}{c}{\textbf{significance}}\\
      \cline{2-16}
                                     & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multicolumn{3}{p{1cm}|}{\hfil $\Random : \Genetic$} & \multicolumn{3}{p{1cm}|}{\hfil $\Random : \RGenetic$} & \multicolumn{3}{p{1cm}}{\hfil $\Genetic : \RGenetic$} \\
      \cline{8-16}
                         & & & & & &                     & L  & M  & S  & L  & M  & S  & L & M & S \\
      \midrule
      \textbf{simple (33)}    & 79 & 97 & 100 & 37  & 9  & 7  & 11 & 12 & 13 & 11 & 13 & 13 & 1 & 1 & 1 \\
      \textbf{difficult (33)} & 58 & 94 & 100 & 112 & 56 & 25 & 22 & 24 & 26 & 22 & 23 & 26 & 2 & 2 & 4 \\
      \midrule
      \textbf{global (56)}    & 63 & 95 & 100 & 88  & 39 & 19 & 33 & 36 & 39 & 33 & 36 & 39 & 3 & 3 & 5 \\
      \bottomrule
    \end{tabular}
\end{table}

@@

% \input{summary_statistics}

@@

\subsection{Search-Based Test Case Generation}
\label{sub.sec.search.based}

@@

\cite{havrikov2014xmlmate} XMLMate: evolutionary XML test generation.

@@

\cite{mairhofer2011search} search-based testing for dynamic languages (Ruby)

@@

>>>>

\usepackage{tablefootnote}
\usepackage{syntax}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{booktabs} % For formal tables
\usepackage{tikz}
\usetikzlibrary{arrows,shadows,positioning,decorations.pathmorphing}
\usepackage{pgf-umlsd}
\usepackage{tikz-uml}
\usepackage{hyperref}
\usepackage{upquote}
\usepackage{listings}
\usepackage{lsthaskell}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage{mdframed}
\usepackage{algorithmic}
\usepackage{longtable}
\usepackage{subcaption}
\usepackage{pgfplots}
\pgfplotsset{compat=newest}
\usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = red, %Colour of internal links
  citecolor    = green %Colour of citations
}

@@

\begin{document}
\title[Search-Based Test Data Generation for JavaScript Functions...]{Search-Based Test Data Generation for JavaScript Functions that Interact with the DOM}

@@

\begin{abstract}
As of 2017 JavaScript and Node.js continue to stay the most prevalent technologies according to the Stack Overflow developers survey. Nevertheless, existing JS testing frameworks are still lacking any support for such a vital step in test automation as the generation of input data. To address this problem, we present a novel \textbf{J}avascript \textbf{E}volutionary-based testing framework with \textbf{D}OM as an \textbf{I}input, called \textbf{JEDI}. In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function including global DOM state. We conducted an empirical evaluation to study the effectiveness and efficiency of our testing framework.
 It has shown that the \emph{genetic with restart} algorithm, proposed in this paper, was able to achieve complete branch coverage on all experimental subjects with the average 19 seconds of execution time per branch.
\end{abstract}

@@

Over the past two decades search-based test data generation has proven to be one of the most effective solutions for a wide range of technologies including object-oriented~\cite{paper}, web~\cite{paper} and mobile~\cite{mao2016sapienz}. In recent years, some effort was made to apply search-based testing to dynamic languages such as Python~\cite{paper}, Ruby~\cite{paper} (maybe mention Go and Lua), but to the best of our knowledge search-based testing approach has never been applied to JavaScript. Our work makes the following contributions:
\begin{enumerate}[leftmargin=5mm]
\item The \emph{JEDI} framework is a novel JS unit testing tool using search-based techniques for generating test data. Notably, our testing framework is able to generate an arbitrary DOM input, which is syntactically valid and compliant with the recent HTML5 specification.   
\item We propose a novel test generation algorithm, called ``genetic with restart'', combining the benefits of systematic fitness improvement with the genetic search and the ability of escaping plateau by restarting search with a new target.
\item Based on the case studies found in two related works~\emph{Confix}~\cite{amin:ase15} and \emph{TAJS}~\cite{dom2011}, we conduced an empirical validation of our framework and performed a significance study of the results. The validation has shown the effectiveness of the framework in covering target branches with a reasonable efficiency...  
\end{enumerate}

@@

\begin{figure}[t!]
\setlength{\grammarparsep}{3pt}
\small
\begin{grammar}

@@

<Array Type> ::= [ <Primitive Type> ] | [ <Array Type> ]
\end{grammar}
\caption{Grammar of supported JS type annotations}
\label{fig.js.type.annot}
\end{figure}
One assumption made in the paper is the availability of type signatures for JS functions. We believe in the legitimacy of such a request due to the following observations. First, typed variants of JS such as \emph{TypeScript}\footnote{\url{https://www.typescriptlang.org/}} are rising in popularity. Second, there has been an active work on the JS type inference done both in academia~\cite{paper} and industry, e.g. Facebook's tool \emph{Flow}\footnote{\url{https://flow.org/}}.

@@

In order to evaluate the feasibility of our test framework adoption in practice, we conducted an empirical evaluation on a set of case-studies described in Section~\ref{sub.sec.case.studies}. All experiments were submitted as a batch mode job on a cluster machine with 32 HT Cores and 256 GB RAM running under Scientific Linux 7.3. We have created three different instances of the JS testing framework --- each is based on a slight variation of the underlying genetic search algorithm. The first version, which play the role of our baseline, is \emph{Random} ($\Random$). Instead of applying crossover and mutation to evolve the population, this algorithm regenerates the new population randomly from scratch. It is worth to notice, that the random version also benefits from both preliminary static analysis phase and dynamic constant propagation as part of the fitness evaluation. The second version is \emph{Genetic}~($\Genetic$) --- it literally follows all of the steps prescribed by the genetic framework in Figure~\ref{fig.framework.architect}. The last version is the \emph{Genetic with Restart} ($\RGenetic$). It is based on the genetic algorithm~\ref{alg.gen} where the search is restarted after the archives are converged within a certain history window. On one hand, the smaller window size forces the GA to converge faster and early discovers the stagnation on a flat space. On the other hand, the small window can lead to a premature archive convergence, which prevents the right genetic combination from been triggered. We have experimented with two different windows of size 5 and 10. But since the latter one ($\RGenetic$) showed the best performance over all, we chose it to report in the paper. Table~\ref{tbl.gen.config} summarizes the configuration parameters for all three versions of the testing framework. The initial setup for genetic algorithm is similar to other frameworks, e.g. \emph{EvoSuite}~\cite{fraser2011evosuite}.

@@

By carrying the evaluation, we would like to address the following research questions:
\begin{description}
\item[\textbf{RQ1 (effectiveness):}] What is the value of branch coverage achieved by our testing framework? Which testing algorithm is the most effective? How the effectiveness changes with the budget per branch?
\item[\textbf{RQ2 (efficiency):}] How much time is needed to cover a branch? What is the cost of one iteration?
\item[\textbf{RQ3 (significance):}] What is the statistical significance and effect size of our experimental results? 
\end{description}

@@

\begin{table}[!t]
  \caption{Result Summary (L - large, M - medium, S - small)}
  \label{tbl.stats.sum}
    \footnotesize
    \begin{tabular}{l|ccc|ccc|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}|p{3mm}p{3mm}p{3mm}}
      \toprule
      \multirow{3}{*}{\textbf{TYPE}} &  \multicolumn{3}{c|}{\textbf{coverage (\%)}} & \multicolumn{3}{c|}{\textbf{time (sec.)}} & \multicolumn{9}{c}{\textbf{significance}}\\
      \cline{2-16}
                                     & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multirow{2}{*}{$\Random$}  & \multirow{2}{*}{$\Genetic$} & \multirow{2}{*}{$\RGenetic$} & \multicolumn{3}{p{1cm}|}{\hfil $_{\Genetic}^{\Random}$} & \multicolumn{3}{p{1cm}|}{\hfil $_{\RGenetic}^{\Random}$} & \multicolumn{3}{p{1cm}}{\hfil $_{\RGenetic}^{\Genetic}$} \\
      \cline{8-16}
                         & & & & & &                     & L  & M  & S  & L  & M  & S  & L & M & S \\
      \midrule
      \textbf{simple (33)}    & 79 & 97 & 100 & 37  & 9  & 7  & 11 & 12 & 13 & 11 & 13 & 13 & 1 & 1 & 1 \\
      \textbf{difficult (33)} & 58 & 94 & 100 & 112 & 56 & 25 & 22 & 24 & 26 & 22 & 23 & 26 & 2 & 2 & 4 \\
      \midrule
      \textbf{global (56)}    & 63 & 95 & 100 & 88  & 39 & 19 & 33 & 36 & 39 & 33 & 36 & 39 & 3 & 3 & 5 \\
      \bottomrule
    \end{tabular}
\end{table}

@@

\paragraph{\textbf{Threats to Validity}}
The \emph{construct validity} threat comes from the measurements we use in our evaluation: branch coverage and execution time. Though, the branch coverage is a common criteria used in practice, the actual fault finding capability is considered a stronger indication of testing adequacy. Reaching a target branch is only part of the problem, we also need an oracle to discriminate the program's output. In this paper, we strike for so called ``natural'' oracles disseminating in exceptions. Using a stronger oracle for validation is future work. Another practical aspect of the test generation is the test case size, since it can both complicate the readability and increase the execution time. To mitigate this issue we configured the GA to start evolution with the candidates of small sizes, which helps to prevent unnecessary data explosion. Additional measure that could be taken is applying a minimization procedure, aka \emph{delta debugging}, to the GA result.

Initial GA configuration introduces the threat to the \emph{internal validity} of our empirical evaluation. The parameters we used are quite standard for similar SBST frameworks, e.g. EvoSuite. Though, not reported in the paper, we performed preliminary assessment of various GA configurations, which confirmed our final decision.

The threat of \emph{conclusion validity} can be affected by the GA stochastic nature. This risk was addressed by repeating the experiment 50 times and performing statistical analysis of the significance and effect size. We used the confidence level of 95\% measured by the Vargha-Delaney statistic and Mann-Whitney U-test.

The \emph{external validity} deals with the threat of generalization of our results due to manual selection of the experimental subjects. To mitigate this fact, we picked the subjects either from previously used in related research or found in open source. Of course, those subjects still have to met the constrains of our testing approach. So, further research is required in both increasing the power of our framework and extending the validation set.

@@

There are several ways how to address the problem of input data generation for JS functions: static and dynamic analysis, symbolic execution, SBST, formal reasoning, the whole web application testing.

\subsection{Search-Based Test Case Generation}

Despite of the practical popularity of JavaScript, the only recorded in the literature attempt of adopting search-based testing for JS unit testing was done by Alshraideh~\cite{alshraideh2008complete}. It uses GA for branch and mutation coverage, but only deals with the limited input types booleans, integers and strings; and provides validation based on one trivial example --- \emph{the triangle program}. On the contrary, our work additionally supports array and DOM types, with suggest reasonable validation with the discussion of significance and effect size. Recently, SBST was applied to other dynamic languages such as Ruby~\cite{mairhofer2011search}, Lua~\cite{wibowo2015unit} and Go~\cite{irawan2016test}, but the treatment of DOM still makes our approach unique.

One likely direction for the future extension of \emph{JEDI} is the whole test suite generation. Most of the time, instead of searching for a test reaching a separate branch, we would like to have a set of tests maximizing the program coverage. That is, our solution is the vector of candidates has the best fitness score in terms of the branch coverage. Usually, such problems incur multi-objective optimization, e.g. coverage vs. test-suite length.

In this paper we dealt with the generation and evolution of DOM which is an example of tree-like data structure. \emph{XMLMATE}~\cite{havrikov2014xmlmate} is a XML test generation tool build on top \emph{EvoSuite} with the aim to improve test coverage of the XML-aware Java programs. To generate random document, it may rely on existing XML schema, or generate document from scratch. In some sense, DOM specification can be thought of a complex XML schema, which is difficult to comply. One distinction of our approach is the use of program analysis for data generation. Both tools have similar philosophy for mutation and crossover. Jan et al.~\cite{jan2016automated} suggest to use XML fuzzing for identifying vulnerabilities in web services.

The \emph{JSContest}~\cite{heidegger2010contract} proposes to annotates JS functions with type-contracts which can guide random test generation. Though the contract language supports the complex objects types, it mostly suitable for primitive inputs, but not DOM. It performs static analysis to collect constant info and feed it to the random generation. We use genetic approach and additionally to collecting static info also perform dynamic analysis during the program execution. Further \emph{JSContest} was extended with the monitoring of \emph{access permission} contracts in~\cite{heidegger2012jscontest}, and the support of reusable DOM fixtures in~\cite{heidegger2010dom}.

Mobile

Object-oriented: EvoSuite~\cite{fraser2011evosuite}

Structural

TODO: discuss multi-objective works and hyper-heuristics search

\label{sub.sec.search.based}

@@

@@

@@

NodEO, a multi-paradigm distributed evolutionary algorithm platform in JavaScript~\cite{merelo2014nodeo}.
